\documentclass[12pt, letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{cite}

% Set double spacing
%\doublespacing

% Formatting for Title, starting halfway down the first page
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{}{0em}{}


\setlength\headheight{24pt}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{Author Last Name: Shortened Title}
\fancyfoot[C]{\thepage}

\begin{document}

\vspace*{2.5in} % Pushes the title halfway down page 1
\begin{center}
    {\LARGE \bfseries Pocket FT8 Transceiver Revisited} \par
    \vspace{0.25in}
    {\large Jim Conrad, KQ7B} \par
    {132 Mill Creek MDW, Grangeville, ID 83530 USA}
\end{center}

\begin{center}
The Pocket FT8 Transceiver Revisited is a portable software defined amateur radio transceiver.
\end{center}

\section{Introduction}
Charles Hill's original Pocket FT8 project has inspired several self-contained FT8 \cite{qstft8} \cite{qexft8} transceiver follow-ons.
This rendition honors the original Pocket FT8 vision with simplified hardware and enhanced firmware features.
The result is a highly portable, single-band, HF transceiver focused on backpacking and mountain day hikes offering:

  \begin{itemize} [noitemsep]
  \item Self-contained --- the radio \textit{is} the computer
  \item Compact board size (4.0X2.8")
  \item FT8 modulation (no CW or SSB)
  \item 275+ mW RF output (QRPP)
  \item Single LP filter slot
  \item 480x320 pixel TFT display
  \item Touchscreen GUI controls
  \item Waterfall display of FT8 traffic
  \item FT8 ``standard" QSO sequencer
  \item Automatic QSO logging to an  ADIF file
  \item JSON station configuration file
  \item Low jitter TCXO
  \item GPS disciplined date, time and location (grid square)
  \item Operation from a single 5V USB power block
  \item Four layer PCB
  \end{itemize}
 

While the feature set purposely constrains the hardware complexity, power consumption and space requirements, the focus on FT8  alone is a compromise.
In its favor, FT8 forgoes the need for the telegraph key, microphone and headset accessories typical of multi-mode transceivers.
By embedding the software defined radio and FT8 on a single board, Pocket FT8 leaves the laptop at home.
Furthermore, FT8's  weak signal performance relaxes the need for ``high" transmit power, enabling an off-the-shelf USB power bank to satisfy the power requirements.
On the other hand, most FT8 QSOs are terse, context-like, exchanges following a  standard sequence with little operator involvement following initiation of the contact.
Alternative designs address situations where this compromise becomes unacceptable.
  
 \section{Hardware}
 \subsection*{Hardware Design}
 \subsection*{FL1 Design}
FL1 mainly provides harmonic rejection for the transmitted signal.
On 40 meters, the five pole Chebyshev design provides for 1 dB of ripple peaking inside the band.

During receive, the Chebyshev low-pass design offers only minimal rejection of out-of-band signals. 
While this has not proven to be a significant issue in the wilderness use-case, the receiver might benefit from a bandpass design in other applications.
 \subsection*{Hardware Construction}

\subsection*{T1}
T1 is a broadband, bifilar wound transformer consisting of 10 turns of 26 AWG on an FT37-43 core.

\subsection*{FL1}
The FL1 low-pass filter can be assembled and tested on a small daughter board.
With some effort, it can probably be made pluggable to facilitate band changes.

\section{Software}
\subsection*{Software Design}

\subsection*{Software Construction}


\section{Testing}

\section{Operation}

\section{Future}

\section{Acknowledgements}


%\newpage
\bibliographystyle{plain}
\bibliography{PocketFT8Revisited}
\end{document}


